% This is LLNCS.DEM the demonstration file of
% the LaTeX macro package from Springer-Verlag
% for Lecture Notes in Computer Science,
% version 2.3 for LaTeX2e
%
\documentclass{llncs}
%
\usepackage{ngerman}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{makeidx}  % allows for indexgeneration
\usepackage{multirow}
\usepackage{rotating}
\usepackage{verbatim}
\usepackage{graphicx}
\usepackage{amssymb}   % AMS-Sonderzeichen
\usepackage{tabularx}  % Für tabularx und newcolumntype
\usepackage[paper=a4paper,left=25mm,right=25mm,top=25mm,bottom=25mm]{geometry}
\usepackage{array}
\usepackage{makecell}
\usepackage{color}
\usepackage{ragged2e}
\usepackage{ifpdf}
% \usepackage{titlesec}
\usepackage{xcolor}    % Lieber xcolor als color. Dann klappt auch das listings gut mit den Farben
\usepackage{listings}
\usepackage{upquote}   % Verändert die Ausgabe der einfachen Anführungszeichen innerhalb von verbatim
\usepackage{eurosym}   % Euro-Zeichen: \euro
\usepackage{lastpage}  % \pageref{LastPage} um die Anzahl der Seiten zu erhalten
% hiermit kann man auch umlaute copy-pasten
\usepackage{lmodern}
\selectlanguage{english}
\usepackage{fancyhdr}
\usepackage{url}
\pagestyle{fancy}


%

\ifpdf
\pdfinfo{
   /Author (Wladymir Alexander Brborich Herrera)
   /Author (Vishwaben Pareshbhai Kakadiya)
   /Author (Hellyben Bhaveshkumar Shah)
   /Author (Priyanka Dilipbhai Vadiwala)
   /Author (Heer Rakeshkumar Vankawala)
   /Title  (LowTech GMmBH Techincal Transformation Milestone 1)
   /Subject (Cloud Computing)
   /Keywords (Cloud Computing, Technical Transformation, Migration)
}
\fi

\setlength{\parindent}{0pt}    % Erste Zeile eines Absatzes nicht einrücken
\parskip2ex                    % Absatzabstand
\setlength{\itemsep}{0ex plus0.2ex}
\sloppy                        % Auf jeden Fall die Seitenränder einhalten.

\newcommand{\what}{LowTech GMmBH Techincal Transformation Milestone 1}
\newcommand{\who}{Group 23}
\newcommand{\when}{WiSe 2024-2025}

\renewcommand{\headrulewidth}{0.4pt}
\renewcommand{\footrulewidth}{0.4pt}
\lhead[\when]{\who}
\rhead[\who]{\when}
\chead[]{}
\lfoot[Page \thepage\ of \pageref{LastPage}]{\what}
\rfoot[\what]{Page \thepage\ of \pageref{LastPage}}
\cfoot[]{}
\pagestyle{fancy}


% Hurenkinder und Schusterjungen komplett verbieten.
\clubpenalty = 10000 
\widowpenalty = 10000 
\displaywidowpenalty = 10000
% Diese Begriffe bezeichnen den Makel beim Textsatz, wenn eine Seite mit der ersten Zeile eines Absatzes endet (so genannter Schusterjunge) oder eine neue Seite mit der letzten Zeile eines Absatzes beginnt (so genanntes Hurenkind).


% Wir definieren ein paar Farben
\definecolor{Brown}{cmyk}{0,0.81,1,0.60}
\definecolor{OliveGreen}{cmyk}{0.64,0,0.95,0.40}
\definecolor{CadetBlue}{cmyk}{0.62,0.57,0.23,0}
\definecolor{lightlightgray}{gray}{0.9}
\definecolor{FrankfurtBlue}{HTML}{3333b2}

% Hier fängt das Dokument an!
\begin{document}

%
% \frontmatter          % for the preliminaries
%
% \tableofcontents
%
\mainmatter              % start of the contributions
%
\title{\what}
%
\author{
  Wladymir Alexander Brborich Herrera\\
  \texttt{wladymir.brborich-herrera@stud.fra-uas.de}
  \and\\ 
  Vishwaben Pareshbhai Kakadiya\\
  \texttt{vishwaben.kakadiya@stud.fra-uas.de}
  \and\\
  Hellyben Bhaveshkumar Shah (1476905)\\
  \texttt{hellyben.shah@stud.fra-uas.de}
  \and\\
  Priyanka Dilipbhai Vadiwala\\
  \texttt{priyanka.vadiwala@stud.fra-uas.de}
  \and\\
  Heer Rakeshkumar Vankawala\\
  \texttt{heer.vankawala@stud.fra-uas.de}
}
%
\institute{
  Frankfurt University of Applied Sciences\\
  (1971-2014: Fachhochschule Frankfurt am Main)\\
  Nibelungenplatz 1\\
  D-60318 Frankfurt am Main\\
}

\maketitle              % typeset the title of the contribution

\begin{abstract}
In this report, we as consultants from \textit{Awesome Cloud AG} present a technical transformation analysis aimed at modernizing the infrastructure of \textit{LowTech GmbH}, 
a small to medium-sized enterprise specializing in wooden furniture production. 
The analysis includes a critical assessment of the current infrastructure, energy consumption calculation for the existing setup 
followed by a detailed transformation roadmap of future-ready modern infrastructure and explanations of enhancements in scalability, availability, and security compared to current infrastructure. 
This analysis will serve as a foundational step for subsequent project phases, ensuring that \textit{LowTech GmbH} is well-equipped to meet future requirements and challenges.
\end{abstract}

\section{Overview of the problem}




\section{Objectives of the technological transformation}


\section{Assessment of the current (as-is) infrastructure}

\subsection{Current traffic and usage}

\subsection{Scalability, Availability and Security Analysis}
According to NIST definition of cloud computing is given as ``Cloud computing is a model for enabling ubiquitous, convenient, on-demand network access to a shared
pool of configurable computing resources (e.g., networks, servers, storage, applications, and services) that
can be rapidly provisioned and released with minimal management effort or service provider interaction.'' \cite{mell2011nist}

As \textit{LowTech GmbH} is based on Legacy IT infrastructure and currently lacking \textit{NIST five
essential characteristics} such as On-demand self-service, Broad network access,Resource pooling,Rapid elasticity and Measured service.

\subsubsection*{Elasticity / Scalability}

\begin{itemize}
  \item \textbf{Fixed Hardware \& Inflexible Infrastructure}:
  \\
  Current infrastructure consists of 7 on-premises servers housed in a single 19-inch rack, 
  along with 17 clients and 19 laptops all with predetermined, static configurations. 
  Moreover, the physical constraints of the on-premises setup, with no additional space for expansion, severely limit scaling options. 
  This inflexibility makes it challenging to accommodate growth or adapt to changing business needs.
 \\
  \item \textbf{Absence of Resource Utilization/pooling}:
  \\ 
  There's no apparent way to quickly scale resources up or down based on demand or user traffic fluctuation in the current infrastructure. 
  Each application typically runs on a dedicated server with fixed resources. 
  This approach leads to inefficient resource utilization, as some servers may be underutilized while others are overloaded which may lead to performance issues during peak times or resource waste during low-demand periods due to no dynamic resource allocation.
 \\
  \item \textbf{Manual Processes \& High Cost}:
  \\ 
  Any changes in capacity would likely require manual hardware upgrades or replacements including hardware installation,
  and configuration, making the process time-consuming and potentially leading to downtime.
  Replacement of hardware is not only tedious but also financially burdensome due to high costs of new hardware.

\end{itemize}

\subsubsection*{Availability}
\begin{itemize}
  \item \textbf{Obsolate Hardware/OS \& Runtime Environments}: 
  \\
  Many components of the current infrastructure is based on very old hardware and outdated operating systems such as 
  Windows XP SP3 (Finance clients), Windows 7 SP3 (HR clients and Customer Service laptops), Debian 5.0 Lenny (Warehouse clients and server),
  Ubuntu 16.04 LTS (Sales CRM Storage server) etc. Several applications are running on outdated software versions such as Java 1.7/1.8, 
  MySQL 5.5/5.7, PHP 5.3 and Firefox 3.6 etc. which makes this whole infrastructure more susceptible to failure.
  \\
  \item \textbf{Lack of Redundancy and Backup Mechanism}:
  \\ 
  There's no mention of redundant systems or data backup solutions which might lead to significant service disruptions as well as data loss in case of any system failure.
  \\
  \item \textbf{Manual Maintainance}: 
  \\It is impossible to meet high availability requirements without a robust failover mechanism due to manual maintenance operations. 
  This increases the possiblity of human errors, leads to longer downtime and reduces overall reliability.
  \\
\end{itemize}
\subsubsection*{Security}

\subsection{Energy consumption and approximate cost}

Energy consumption calculation for the as-in infrastructure of Low Tech GmbH is as follows : 

\begin{table}[htbp]
\centering
\begin{tabular}{|l|c|c|c|c|c|}
\hline
\textbf{Departments} & \textbf{Server} & \textbf{Client} & \textbf{Laptop} & \textbf{Total Power} & \textbf{Annual Energy}  \\
 & \textbf{ (Qty x Power) } & \textbf{ (Qty x Power) } & \textbf{ (Qty x Power) } & \textbf{ Consumption } & \textbf{ Consumption(KWh) } \\
\hline
Finance & 1 x 1000W & 4 x 500W & - & 3000W & 26,280 \\
\hline
HR & 1 x 1000W & 3 x 500W & - & 2500W & 21,900 \\
\hline
Warehouse & 1 x 1000W & 10 x 500W & - & 6000W & 52,560 \\
\hline
Sales & \makecell{1 x 1000W \\ 1 x 1200W} & - & 10 x 50W & 2700W & 23,652 \\
\hline
Operations & 1 x 1200W & - & 4 x 50W & 1400W & 12,264\\
\hline
Customer Service & - & - & 5 x 100W & 500W & 4,380 \\
\hline
Webshop & 1 x 1200W & - & - & 1200W & 10,512\\
\hline
\end{tabular}
\caption{Power Consumption by Department and Device Type}
\label{tab:power_consumption}
\end{table}

\textbf{Total Energy Consumption (Annual)} : 151,548 KWh (151.548 MWh)

According to Eurostat published data of electricity prices for non-household consumers \cite{eurostat2023}, Low Tech GmbH falls under the annual energy consumption band 
`IB (20 MWh to 499 MWh)' with energy price 0.3244 \EUR{} per KWh.


\textbf{Total Cost for Energy Consumption (Annual)} : 151,548 KWh x 0.3244 \EUR{} = 49,162.17 \EUR{}


\section{Client Requirements}

\section{Assessment of potential technological components}

\subsection{Hardware}

\subsection{Virtualization technologies}


\subsection{Application components}

\subsection{Platforms}

\subsection{Security components}


\section{Migration to a private-cloud context}

\subsection{Selected technologies}

\subsection{Architecture}

\subsection{Roadmap}

\subsection{Operation considerations}

% ---- Bibliography ----

\begin{thebibliography}{5}
  
  \bibitem{eurostat2023}
Eurostat. (2023). \textit{Electricity prices for non-household consumers - bi-annual data (from 2007 onwards)}. Retrieved November 16, 2023, from \url{https://ec.europa.eu/eurostat/databrowser/view/nrg_pc_205__custom_13581723/default/table?lang=en}

\bibitem{mell2011nist}
Mell, P. and Grance, T. (2011).
\emph{The NIST definition of cloud computing}.
National Institute of Standards and Technology, Special Publication 800-145, Gaithersburg, MD.
\url{https://nvlpubs.nist.gov/nistpubs/Legacy/SP/nistspecialpublication800-145.pdf} 

\end{thebibliography}
\end{document}
